---
title: "Preliminary Analysis of Focused Attention Data"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(stringr)

setwd("~/BT010_FA_Analysis/")
data = read_csv("./data/feature_data.csv")
source("helpers.R")
options(width = 90)
```

```{r, message=FALSE, echo=FALSE}
responses = c(
    "log_ecg_heart_rate_mean", "log_ecg_hrv_std_mean", "skin_temperature_mean", 
    "eda_mean_mean", "log_eda_no_of_peaks_mean", "log_eda_lf_mean", "log_eda_hf_mean", 
    "log_eda_lf_hf_ratio_mean"
)

ecg_dat = data %>% 
    mutate(
        ecg_heart_rate_mean = ifelse(
            ecg_heart_rate_mean < 50, NA, ecg_heart_rate_mean
        ), 
        ecg_hrv_std_mean = ifelse(
            ecg_hrv_std_mean > 250, NA, ecg_hrv_std_mean
        ), 
        skin_temperature_mean = ifelse(
            skin_temperature_mean < 25, NA, skin_temperature_mean
        ), 
        log_ecg_heart_rate_mean = log(ecg_heart_rate_mean),
        log_ecg_hrv_std_mean = log(ecg_hrv_std_mean),
        log_eda_hf_mean = log(eda_hf_mean), 
        log_eda_lf_mean = log(eda_lf_mean), 
        log_eda_lf_hf_ratio_mean = log(eda_lf_hf_ratio_mean),
        log_eda_no_of_peaks_mean = log(eda_no_of_peaks_mean)
    ) %>%
    rename(
        pid = Participant, 
        type = Type
    ) %>%
    select(
        pid, type, Difficulty, Perceptibility, context_order, one_of(responses)
    ) %>% 
    mutate(
        time = as.factor(context_order), 
        pid = as.factor(pid), 
        type = as.factor(type), 
        difficulty = as.factor(ifelse(Difficulty == 0, 'L', 'H')), 
        perceptibility = as.factor(ifelse(Perceptibility == 0, 'L', 'H'))
    ) %>%
    select(-context_order, - Difficulty, -Perceptibility)
```

# Summary

This document contains an analysis of the Focused Attention data using [Model
3](https://rndtools.uhgrd.com/Print/InitiativeDocument/1090/MVP%20FA_data%20analysis%20plan_10.04.19_gka.pdf)
on the [original feature
list](https://rndtools.uhgrd.com/Project/Initiative/502#) which was provided
before the start of the current
[BT010-FA](https://rndtools.uhgrd.com/Project/Initiative/502) initiative.  The
results show that, for four of eight features, VR leads to a different
physiological response compared to 2D, but only one feature seems to be
materially effected by game difficulty. Consequently, this analysis provides
little guidance on how game parameters can be manipulated to keep a patient's
stress response in a prespecified range using the current feature set. Next
steps for the initiative would be to explore new features that
may be associated with stress response.

# Results

For each feature, we show Type III sum of squares, all pairwise differences for
the three-way treatment interactions, the difference in difference of
physiological response between treatments delivered in 2D versus VR, and a plot
of raw and fitted patient data with a 95% bootstrapped confidence interval for
the respective mean. We dropped mean heart rate readings below 50, heart rate
variability above 250, and skin temperature readings below 25 degrees celsius
from the analysis, and log transformed most features to meet the normality
assumptions for an ANOVA. Only the pairwise contrasts adjust for multiple
comparisons (using Tukeys method), and this adjustment is made on the feature
level, i.e. there are no adjustments for the fact that we conduct the analysis
on eight different physiological features. The effects for game difficulty and
perceptibility are not significant for most features; consequently, the results
of our analysis do not provide clear support for the hypothesis that game
parameters can be manipulated to keep a patient's stress response in a
prespecified range.

In our final analysis for the initiative, we need to adequately deal with
outliers and bad data; for example, a heart rate of less than 25 is likely an
erroneous data point. We need to agree upon ranges for parameters which make
scientific sense, i.e. heart rate between 50 and 200, skin temperature above 25
degrees celsius, etc.  As we go to real-time feature creation in our biofeedback
pilots, adequate plans for dealing with erroneous data are needed. We ask that
these ranges are included in the list of parameters that the Research team is
expected to provide as part of deliverable two in grant one of
[BT010-FA](https://rndtools.uhgrd.com/Project/Initiative/502).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
for(i in 1:length(responses))
{
    resp = responses[i]
    formula_string = paste0(
        resp, " ~ (1|pid) + time + type*difficulty*perceptibility"
    )
    glm_dat_lme4 = lme4::lmer(as.formula(formula_string), data = ecg_dat)
    glm_dat_lmerTest = lmerTest::lmer(as.formula(formula_string), data = ecg_dat)
    cat("################################################################### \n")
    cat("The response/dependent variable is:", resp, "\n")
    cat("################################################################### \n")
    cat("#**************************************************# \n")
    cat("ANOVA Table \n")
    cat("#**************************************************# \n")
    anova(glm_dat_lmerTest, type = "III") %>% print()
    cat("#**************************************************# \n")
    cat("All third order pairwise contrasts \n")
    cat("Symbol order is Type:Diff:Percp \n")
    cat("#**************************************************# \n")
    emmeans(glm_dat_lme4, 
            specs = pairwise ~ type:difficulty:perceptibility
        )$contrasts  %>%
        tbl_df(.) %>%
        print(n = 50)
    cat("#**************************************************# \n")
    cat("Difference in difference (2D - 3D) \n")
    cat("HL means Difficulty is High and Percept is Low \n")
    cat("Lower and Upper are from bootstrapped 95% CIs \n")
    cat("#**************************************************# \n")
    get_diff_in_diff(ecg_dat, glm_dat_lme4, resp,n_sim = 100) %>% print()
    plots = make_interaction_plot(ecg_dat, resp, glm_dat_lme4) 
    print(plots[[1]])
    print(plots[[2]])
}
```

