---
title: "Technology Attitude and VR Experience Exploration"
author: "__Gwyn Omar Magoncia__"
date: _Last Updated:_ `r format(Sys.time(), '%B %d, %Y')`
output: 
  pdf_document:
    number_sections: true
---

```{r loading-libraries-and-reading-data, include = FALSE}
knitr::opts_chunk$set(comment = NA, echo = FALSE, warning = FALSE, message = FALSE)
library('here')
library('data.table')
library('magrittr')
library('kableExtra')
library('ggplot2')
library('Kendall')
library('DescTools')

geq_scoring <- fread(here::here("Data", "geq.csv"))
mtuas <- fread(here::here("Data", "mtuas.csv"))
```

```{r sourcing-functions}
source(here::here("R", "theme.R"))
source(here::here("R", "plot_functions.R"))
source(here::here("R", "table_to_df_function.R"))
```

```{r data-prep}
geq_scoring[, ID := as.numeric(substr(Q3, 11, 12))]
setkey(geq_scoring, ID)
setnames(geq_scoring, 'Q3', 'PID')

mtuas[, ID := as.numeric(substr(Q11, 11, 12))] %>%
    .[, Q9_10 := 6 - Q9_10, keyby = .(ID)] %>% # reverse scoring the negative items 
    .[, Q9_11 := 6 - Q9_11, keyby = .(ID)] %>% # reverse scoring the negative items 
    .[, Q9_12 := 6 - Q9_12, keyby = .(ID)] %>% # reverse scoring the negative items 
    .[, SC16 := sum(c(Q9_1, Q9_2, Q9_3, Q9_7, Q9_8, Q9_9, Q9_10, Q9_11, Q9_12)), 
      keyby = .(ID)] %>% # total score for attitude towards technology 
    .[, SC16_mean := mean(c(Q9_1, Q9_2, Q9_3, Q9_7, Q9_8, Q9_9, Q9_10, Q9_11, Q9_12)), 
      keyby = .(ID)] %>% # mean score for attitude towards technology
    .[, SC16_median := median(c(Q9_1, Q9_2, Q9_3, Q9_7, Q9_8, Q9_9, Q9_10, Q9_11, Q9_12)), 
      keyby = .(ID)] %>% # median score for attitude towards technology
    .[, TA_mean := ifelse(SC16_mean <= 2, "Negative", # tech attitude using mean approach
                          ifelse(SC16_mean >= 4, "Positive", "Mixed"))] %>%
    .[, TA_median := ifelse(SC16_median <= 2, "Negative", # tech attitude using median approach
                            ifelse(SC16_median >= 4, "Positive", "Mixed"))] %>%
    .[, TA_mean := factor(TA_mean, levels = c("Negative", "Mixed", "Positive"))] %>%
    .[, TA_median := factor(TA_median, levels = c("Negative", "Mixed", "Positive"))]
setkey(mtuas, ID)
# getting key variables from the MTUAS table
mtuas_var <- mtuas[, .(Q11, Q12, Q13, ID, SC16, SC16_mean, SC16_median, TA_mean, TA_median)]
setnames(mtuas_var, old = c('Q11','Q12', 'Q13'), new = c('PID', 'Gender', 'Age'))

cols1 <- c(41:42)
cols2 <- c(7:37)
geq_mtuas <- merge(geq_scoring, mtuas_var, by = c('PID', 'ID'), all = TRUE) %>%
                 .[!is.na(Q4),] %>% # Only 31 IDs, ID number 10 is missing
                 .[, Q2_2_rev := 6 - Q2_2, keyby = .(ID)] %>% # reverse scoring the negative items
                 .[, Q2_4_rev := 6 - Q2_4, keyby = .(ID)] %>%  
                 .[, Q2_6_rev := 6 - Q2_6, keyby = .(ID)] %>%  
                 .[, Q2_11_rev := 6 - Q2_11, keyby = .(ID)] %>%   
                 .[, Q2_14_rev := 6 - Q2_14, keyby = .(ID)] %>% 
                 .[, Q2_15_rev := 6 - Q2_15, keyby = .(ID)] %>% 
                 .[, SC3 := sum(c(Q2_1, Q2_5, Q2_7, Q2_8, Q2_12, # total score for VR experience
                                  Q2_16, Q2_2_rev, Q2_4_rev, Q2_6_rev, 
                                  Q2_11_rev, Q2_14_rev, Q2_15_rev)), 
                   keyby = .(ID, Q4)] %>% 
                 .[, SC3_mean := mean(c(Q2_1, Q2_5, Q2_7, Q2_8, # mean score for VR experience
                                        Q2_12, Q2_16, Q2_2_rev, Q2_4_rev, 
                                        Q2_6_rev, Q2_11_rev, Q2_14_rev, Q2_15_rev)), 
                   keyby = .(ID, Q4)] %>% 
                 .[, SC3_median := median(c(Q2_1, Q2_5, Q2_7, Q2_8, # median score for VR experience
                                            Q2_12, Q2_16, Q2_2_rev, Q2_4_rev, 
                                            Q2_6_rev, Q2_11_rev, Q2_14_rev, Q2_15_rev)), 
                   keyby = .(ID, Q4)] %>% 
                 .[, VR_mean := ifelse(SC3_mean <= 2, "Negative", # VR Exp using mean approach
                                       ifelse(SC3_mean >= 4, "Positive", "Mixed"))] %>%
                 .[, VR_median := ifelse(SC3_median <= 2, "Negative", # VR Exp using median appoach
                                         ifelse(SC3_median >= 4, "Positive", "Mixed"))] %>%
                 .[, VR_mean := factor(VR_mean, levels = c("Negative", "Mixed", "Positive"))] %>%
                 .[, VR_median := factor(VR_median, 
                                         levels = c("Negative", "Mixed", "Positive"))] %>%
                 .[, (cols1) := lapply(.SD, as.factor), .SDcols = cols1] %>%
                 .[, (cols2) := lapply(.SD, factor, levels = c("1", "2", "3", "4", "5"), 
                                       labels = c("Not at all", "Slightly", "Moderately", 
                                                  "Fairly", "Extremely")), .SDcols = cols2]

levels(geq_mtuas$Age) <- c("18-30", "31-40", "41-50", "51-60", "61-70", "70+")
levels(geq_mtuas$Gender) <- c("Male", "Female")

geq_mtuas_go <- geq_mtuas[Q4 <= 4,] # Oculus Go VR headset
geq_mtuas_rift <- geq_mtuas[Q4 > 4,] # Oculus Rift VR headset
```

# __Introduction__

This report contains the analysis of the Game Experience Questionnaire (GEQ) survey data. Currently, 
the GEQ contains only the in-game and post-game modules. In this analysis, we will see how our 
patient pool perceive virtual reality (VR) using two VR headsets, Oculus Go and Oculus Rift.

# __Methods__

## __Study Sample__

32 patients went through a VR experiment at the Southwest Medical Associates (SMA) clinic in Las 
Vegas, NV. Upon close inspection of the GEQ data, one patient was missing while the rest were
divided into two groups based on the type of VR headsets used. 31 patients used Oculus Go while 18 
used Oculus Rift.

## __Scoring__

```{r scoring}
tbl_01 <- c("1", "Strongly disagree", "Not at all", 
            "5", "Strongly agree", "Extremely")
tbl_02 <- c("2", "Disagree", "Slightly", 
            "4", "Agree", "Fairly")
tbl_03 <- c("3", "Neither agree\nnor disagree", "Moderately",
            "3", "Neither agree\nnor disagree", "Moderately")
tbl_04 <- c("4", "Agree", "Fairly",
            "2", "Disagree", "Sightly")
tbl_05 <- c("5", "Strongly agree", "Extremely",
            "1", "Strongly disagree", "Not at all")

tbl <- ls(pattern = "tbl_")
score_df <- as.data.frame(do.call(rbind, lapply(tbl, get)))
rm(list = ls(pattern = "tbl_"))
colnames(score_df) <- c("Scale", "Technology Attitude", "VR Game Experience",
                        "Scale", "Technology Attitude", "VR Game Experience")

score_df %>%
  kable(align = c("c", "c", "c", "c", "c"), caption = "Reverse Scoring of Negative Items") %>%
  add_header_above(c("Original" = 3, "New" = 3)) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

## __Chi-Square Test__

\clearpage

# __Results__

## __Technology Attitude__

```{r tech-attitude-go-median}
TA_go <- geq_mtuas_go[, .(Count = .N), keyby = .(TA_median)] %>% 
                    .[, .(TA_median, Count, 
                          Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(TA_go, "TA_median", "Technology Attitude")

TA_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r tech-attitude-go-median-gender}
TA_go_gender <- geq_mtuas_go[, .(Count = .N), keyby = .(Gender, TA_median)] %>% 
                           .[, .(TA_median, Gender, Count, 
                                 Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(TA_go_gender, "TA_median", "Technology Attitude")

TA_go_gender %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown by Gender for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r tech-attitude-go-median-age}
TA_go_age <- geq_mtuas_go[, .(Count = .N), keyby = .(Age, TA_median)] %>% 
                        .[, .(TA_median, Age, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(TA_go_age, "TA_median", "Technology Attitude")

TA_go_age %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown by Age for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

```{r tech-attitude-rift-median}
TA_rift <- geq_mtuas_rift[, .(Count = .N), keyby = .(TA_median)] %>% 
                        .[, .(TA_median, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(TA_rift, "TA_median", "Technology Attitude")

TA_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r tech-attitude-rift-median-gender}
TA_rift_gender <- geq_mtuas_rift[, .(Count = .N), keyby = .(Gender, TA_median)] %>% 
                               .[, .(TA_median, Gender, Count, 
                                     Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(TA_rift_gender, "TA_median", "Technology Attitude")

TA_rift_gender %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown by Gender for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r tech-attitude-rift-median-age}
TA_rift_age <- geq_mtuas_rift[, .(Count = .N), keyby = .(Age, TA_median)] %>% 
                            .[, .(TA_median, Age, Count, 
                                  Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(TA_rift_age, "TA_median", "Technology Attitude")

TA_rift_age %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown by Age for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

## __VR Game Experience__

```{r vr-exp-go-median}
VR_go <- geq_mtuas_go[, .(Count = .N), keyby = .(VR_median)] %>% 
                    .[, .(VR_median, Count, 
                          Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(VR_go, "VR_median", "VR Game Experience")

VR_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r vr-exp-go-median-gender}
VR_go_gender <- geq_mtuas_go[, .(Count = .N), keyby = .(Gender, VR_median)] %>% 
                           .[, .(VR_median, Gender, Count, 
                                 Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(VR_go_gender, "VR_median", "VR Game Experience")

VR_go_gender %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown by Gender for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r vr-exp-go-median-age}
VR_go_age <- geq_mtuas_go[, .(Count = .N), keyby = .(Age, VR_median)] %>% 
                        .[, .(VR_median, Age, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(VR_go_age, "VR_median", "VR Game Experience")

VR_go_age %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown by Age for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

```{r vr-exp-rift-median}
VR_rift <- geq_mtuas_rift[, .(Count = .N), keyby = .(VR_median)] %>% 
                        .[, .(VR_median, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(VR_rift, "VR_median", "VR Game Experience")

VR_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r vr-exp-rift-median-gender}
VR_rift_gender <- geq_mtuas_rift[, .(Count = .N), keyby = .(Gender, VR_median)] %>% 
                               .[, .(VR_median, Gender, Count, 
                                     Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(VR_rift_gender, "VR_median", "VR Game Experience")

VR_rift_gender %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown by Gender for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r vr-exp-rift-median-age}
VR_rift_age <- geq_mtuas_rift[, .(Count = .N), keyby = .(Age, VR_median)] %>% 
                            .[, .(VR_median, Age, Count, 
                                  Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(VR_rift_age, "VR_median", "VR Game Experience")

VR_rift_age %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown by Age for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

__Contingency Table__

```{r contingency-table-go-median}
tbl_go <- table(geq_mtuas_go$TA_median, geq_mtuas_go$VR_median)
chisq_go <- chisq.test(tbl_go) 
table_to_df("go", tbl_go, chisq_go)
```

```{r contingency-table-rift-median}
tbl_rift <- table(geq_mtuas_rift$TA_median, geq_mtuas_rift$VR_median)
chisq_rift <- chisq.test(tbl_rift) 
table_to_df("rift", tbl_rift, chisq_rift)
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge GEQ Post-game - Oculus Go}
\vfill

\clearpage

```{r post-game-go-q1-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_1, "Q2_1", geq = 2, i = 1)
```

\vspace{1em} 

```{r post-game-go-q2-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_2, "Q2_2", geq = 2, i = 2)
```

\clearpage

```{r post-game-go-q3-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_3, "Q2_3", geq = 2, i = 3)
```

\vspace{1em}

```{r post-game-go-q4-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_4, "Q2_4", geq = 2, i = 4)
```

\clearpage

```{r post-game-go-q5-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_5, "Q2_5", geq = 2, i = 5)
```

\vspace{1em}

```{r post-game-go-q6-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_6, "Q2_6", geq = 2, i = 6)
```

\clearpage

```{r post-game-go-q7-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_7, "Q2_7", geq = 2, i = 7)
```

\vspace{1em}

```{r post-game-go-q8-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_8, "Q2_8", geq = 2, i = 8)
```

\clearpage

```{r post-game-go-q9-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_9, "Q2_9", geq = 2, i = 9)
```

\vspace{1em}

```{r post-game-go-q10-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_10, "Q2_10", geq = 2, i = 10)
```

\clearpage

```{r post-game-go-q11-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_11, "Q2_11", geq = 2, i = 11)
```

\vspace{1em}

```{r post-game-go-q12-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_12, "Q2_12", geq = 2, i = 12)
```

\clearpage

```{r post-game-go-q13-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_13, "Q2_13", geq = 2, i = 13)
```

\vspace{1em}

```{r post-game-go-q14-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_14, "Q2_14", geq = 2, i = 14)
```

\clearpage

```{r post-game-go-q15-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_15, "Q2_15", geq = 2, i = 15)
```

\vspace{1em}

```{r post-game-go-q16-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_16, "Q2_16", geq = 2, i = 16)
```

\clearpage

```{r post-game-go-q17-tech-attitude}
plot_tech_attitude(geq_mtuas_go, Q2_17, "Q2_17", geq = 2, i = 17)
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge GEQ Post-game - Oculus Rift}
\vfill

\clearpage

```{r post-game-rift-q1-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_1, "Q2_1", geq = 2, i = 1)
```

\vspace{1em} 

```{r post-game-rift-q2-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_2, "Q2_2", geq = 2, i = 2)
```

\clearpage

```{r post-game-rift-q3-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_3, "Q2_3", geq = 2, i = 3)
```

\vspace{1em}

```{r post-game-rift-q4-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_4, "Q2_4", geq = 2, i = 4)
```

\clearpage

```{r post-game-rift-q5-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_5, "Q2_5", geq = 2, i = 5)
```

\vspace{1em}

```{r post-game-rift-q6-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_6, "Q2_6", geq = 2, i = 6)
```

\clearpage

```{r post-game-rift-q7-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_7, "Q2_7", geq = 2, i = 7)
```

\vspace{1em}

```{r post-game-rift-q8-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_8, "Q2_8", geq = 2, i = 8)
```

\clearpage

```{r post-game-rift-q9-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_9, "Q2_9", geq = 2, i = 9)
```

\vspace{1em}

```{r post-game-rift-q10-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_10, "Q2_10", geq = 2, i = 10)
```

\clearpage

```{r post-game-rift-q11-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_11, "Q2_11", geq = 2, i = 11)
```

\vspace{1em}

```{r post-game-rift-q12-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_12, "Q2_12", geq = 2, i = 12)
```

\clearpage

```{r post-game-rift-q13-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_13, "Q2_13", geq = 2, i = 13)
```

\vspace{1em}

```{r post-game-rift-q14-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_14, "Q2_14", geq = 2, i = 14)
```

\clearpage

```{r post-game-rift-q15-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_15, "Q2_15", geq = 2, i = 15)
```

\vspace{1em}

```{r post-game-rift-q16-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_16, "Q2_16", geq = 2, i = 16)
```

\clearpage

```{r post-game-rift-q17-tech-attitude}
plot_tech_attitude(geq_mtuas_rift, Q2_17, "Q2_17", geq = 2, i = 17)
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge Appendix}
\vfill

\clearpage

## __Technology Attitude__

```{r tech-attitude-go-mean}
TA_go <- geq_mtuas_go[, .(Count = .N), keyby = .(TA_mean)] %>% 
                    .[, .(TA_mean, Count, 
                          Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(TA_go, "TA_mean", "Technology Attitude")

TA_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r tech-attitude-rift-mean}
TA_rift <- geq_mtuas_rift[, .(Count = .N), keyby = .(TA_mean)] %>% 
                        .[, .(TA_mean, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(TA_rift, "TA_mean", "Technology Attitude")

TA_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "Technology Attitude Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

## __VR Game Experience__

```{r vr-exp-go-mean}
VR_go <- geq_mtuas_go[, .(Count = .N), keyby = .(VR_mean)] %>% 
                    .[, .(VR_mean, Count, 
                          Percentage = round(Count * 100 / nrow(geq_mtuas_go), 1))]
setnames(VR_go, "VR_mean", "VR Game Experience")

VR_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r vr-exp-rift-mean}
VR_rift <- geq_mtuas_rift[, .(Count = .N), keyby = .(VR_mean)] %>% 
                        .[, .(VR_mean, Count, 
                              Percentage = round(Count * 100 / nrow(geq_mtuas_rift), 1))]
setnames(VR_rift, "VR_mean", "VR Game Experience")

VR_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "VR Game Experience Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

__Contingency Table__

```{r contingency-table-go-mean}
tbl_go <- table(geq_mtuas_go$TA_mean, geq_mtuas_go$VR_mean)
chisq_go <- chisq.test(tbl_go) 
table_to_df("go", tbl_go, chisq_go)
```

```{r contingency-table-rift-mean}
tbl_rift <- table(geq_mtuas_rift$TA_mean, geq_mtuas_rift$VR_mean)
chisq_rift <- chisq.test(tbl_rift) 
table_to_df("rift", tbl_rift, chisq_rift)
```



