---
title: "Game Experience Questionnaire Exploration"
author: "__Joyvalerie Mondejar, Gwyn Omar Magoncia__"
date: _Last Updated:_ `r format(Sys.time(), '%B %d, %Y')`
output: 
  pdf_document:
    number_sections: true
---

```{r loading-libraries-and-reading-data, include = FALSE}
knitr::opts_chunk$set(comment = NA, echo = FALSE, warning = FALSE, message = FALSE)
library('here')
library('data.table')
library('magrittr')
library('kableExtra')
library('ggplot2')

geq_scoring <- fread(here::here("Data", "geq.csv"))
mtuas <- fread(here::here("Data", "mtuas.csv"))
mtuas_cluster <- readRDS(here::here("Data", "mtuas_cluster.rds"))
```

```{r sourcing-functions}
source(here::here("R", "theme.R"))
source(here::here("R", "plot_functions.R"))
```

```{r data-prep, include=FALSE}
geq_scoring[, ID := as.numeric(substr(Q3, 11, 12))]
setkey(geq_scoring, ID)
setnames(geq_scoring, 'Q3', 'PID')

mtuas_cluster[, ID := as.numeric(substr(Q11, 11, 12))]
setkey(mtuas_cluster, ID)
# getting age and gender from the GEQ file
mtuas_demog <- mtuas_cluster[, .(Q11, Gender, Age, ID, Group)] %>%
                           .[, Group := factor(Group, levels = c("1", "2", "3"))]

setnames(mtuas_demog, 'Q11', 'PID')

cols1 <- c(41:42)
cols2 <- c(7:37)
geq_scoring <- merge(geq_scoring, mtuas_demog, by = c('PID', 'ID'), all = TRUE) %>%
                   .[!is.na(Q4),] %>% # Only 31 IDs, ID number 10 is missing
                   .[, IGC1 := mean(c(Q1_2, Q1_9)), keyby = .(ID, Q4)] %>%
                   .[, IGC2 := mean(c(Q1_1, Q1_4)), keyby = .(ID, Q4)] %>%
                   .[, IGC3 := mean(c(Q1_5, Q1_10)), keyby = .(ID, Q4)] %>%
                   .[, IGC4 := mean(c(Q1_6, Q1_8)), keyby = .(ID, Q4)] %>%
                   .[, IGC5 := mean(c(Q1_12, Q1_13)), keyby = .(ID, Q4)] %>%
                   .[, IGC6 := mean(c(Q1_3, Q1_7)), keyby = .(ID, Q4)] %>%
                   .[, IGC7 := mean(c(Q1_11, Q1_14)), keyby = .(ID, Q4)] %>%
                   .[, PGC1 := mean(c(Q2_1, Q2_5, Q2_7, Q2_8, Q2_12, Q2_16)), 
                     keyby = .(ID, Q4)] %>%
                   .[, PGC2 := mean(c(Q2_2, Q2_4, Q2_6, Q2_11, Q2_14, Q2_15)), 
                     keyby = .(ID, Q4)] %>%
                   .[, PGC3 := mean(c(Q2_10, Q2_13)), keyby = .(ID, Q4)] %>%
                   .[, PGC4 := mean(c(Q2_3, Q2_9, Q2_17)), keyby = .(ID, Q4)] %>%
                   .[, (cols1) := lapply(.SD, as.factor), .SDcols = cols1] %>%
                   .[, (cols2) := lapply(.SD, factor, levels = c("1", "2", "3", "4", "5"),
                                         labels = c("Not at all", "Slightly", "Moderately", 
                                         "Fairly", "Extremely")), .SDcols = cols2]
                   

levels(geq_scoring$Age) <- c("18-30", "31-40", "41-50", "51-60", "61-70", "70+")
levels(geq_scoring$Gender) <- c("Male", "Female")

geq_scoring_go <- geq_scoring[Q4 <= 4,] # Oculus Go VR headset
geq_scoring_rift <- geq_scoring[Q4 > 4,] # Oculus Rift VR headset
```

# __Introduction__

This report contains the analysis of the Game Experience Questionnaire (GEQ) survey data. Currently, 
the GEQ contains only the in-game and post-game modules. In this analysis, we will see how our 
patient pool perceive virtual reality (VR) using two VR headsets, Oculus Go and Oculus Rift.

# __Study Sample__

32 patients went through a VR experiment at the Southwest Medical Associates (SMA) clinic in Las 
Vegas, NV. Upon close inspection of the GEQ data, one patient was missing while the rest were
divided into two groups based on the type of VR headsets used. 31 patients used Oculus Go while 18 
used Oculus Rift.

# __Results__

This section is divided into three parts: Demographics, Components, and Plots. The first part
contains the age group and gender breakdown under both VR headset groups. The second part contains 
the median component scores for the two modules under both groups. The last part contains individual 
plots for the responses of both groups on all questions of the two modules. The responses are broken 
down based on gender and age groups.

\clearpage

## __Demographics__

For both groups, there are more female than male patients and majority of these patients belong
to the 51-60 age group.

```{r gender-go}
gender_go <- geq_scoring_go[, .(Count = .N), keyby = .(Gender)] %>%
                          .[, .(Gender, Count, 
                                Percentage = round(Count * 100 / nrow(geq_scoring_go), 1))]

gender_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "Gender Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r gender-rift}
gender_rift <- geq_scoring_rift[, .(Count = .N), keyby = .(Gender)] %>% 
                              .[, .(Gender, Count, 
                                    Percentage = round(Count * 100 / nrow(geq_scoring_rift), 1))]

gender_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "Gender Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r age-go}
age_go <- geq_scoring_go[, .(Count = .N), keyby = .(Age)] %>%
                       .[, .(Age, Count, 
                             Percentage = round(Count * 100 / nrow(geq_scoring_go), 1))]

age_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "Age Group Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r age-rift}
age_rift <- geq_scoring_rift[, .(Count = .N), keyby = .(Age)] %>% 
                           .[, .(Age, Count, 
                                 Percentage = round(Count * 100 / nrow(geq_scoring_rift), 1))]

age_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "Age Group Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

## __Component Scores__

For both modules, the median component scores for both groups are close to each other except for the 
challenge component in the in-game module wherein the Oculus Rift group has a higher median score 
than the Oculus Go group which implies that the users in the former group are having a hard time
with the Oculus Rift VR headset.

Overall, users from both groups have a positive experience with VR. However, the median scores for
the positive experience of the in-game module are higher compared to the post-game module. This is 
mostly due to the number of items considered in computing the average scores for these components, 
two for the in-game positive affect component while six for the positive experience component.

```{r in-game-comp-scores}
ig_comp_score_go <- unique(geq_scoring_go[, c(44:50)] %>%
                                        .[, lapply(.SD, function(x) {round(mean(x), 1)}), 
                                          .SDcols = 1:7])
ig_comp_score_rift <- unique(geq_scoring_rift[, c(44:50)] %>%
                                            .[, lapply(.SD, function(x) {round(mean(x), 1)}), 
                                              .SDcols = 1:7])
comp_score <- as.data.frame(cbind(t(ig_comp_score_go), t(ig_comp_score_rift)))
rownames(comp_score) <- NULL
comp <- as.data.frame(rbind("Competence", "Sensory and Imaginative Immersion", "Flow",
                            "Tension", "Challenge", "Negative affect", "Positive affect"))
ig_comp_score <- cbind(comp, comp_score)
colnames(ig_comp_score) <- c("Component", "Oculus Go VR Headset", "Oculus Rift VR Headset")

ig_comp_score %>%
  kable(align = c("l", "c", "c"), 
        caption = "In-game Mean Component Scores of Oculus Go vs. Oculus Rift") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r post-game-comp-scores}
pg_comp_score_go <- unique(geq_scoring_go[, c(51:54)] %>%
                                        .[, lapply(.SD, function(x) {format(round(mean(x), 1), 
                                                                            nsmall = 1)}), 
                                          .SDcols = 1:4])
pg_comp_score_rift <- unique(geq_scoring_rift[, c(51:54)] %>%
                                            .[, lapply(.SD, function(x) {format(round(mean(x), 1), 
                                                                            nsmall = 1)}), 
                                              .SDcols = 1:4])
comp_score <- as.data.frame(cbind(t(pg_comp_score_go), t(pg_comp_score_rift)))
rownames(comp_score) <- NULL
comp <- as.data.frame(rbind("Positive Experience", "Negative Experience",
                            "Tiredness", "Returning to Reality"))
pg_comp_score <- cbind(comp, comp_score)
colnames(pg_comp_score) <- c("Component", "Oculus Go VR Headset", "Oculus Rift VR Headset")

pg_comp_score %>%
  kable(align = c("l", "c", "c"), 
        caption = "Post-game Mean Component Scores of Oculus Go vs. Oculus Rift") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

## __Clustering__

Pprincipal component analysis (PCA) was used on the technology attitude questions and k-means 
clustering was used to cluster the individuals into three clusters based on their attitude towards
technology. Here are the descriptions for each cluster:

* Cluster 1 consists of members having consistently high positive attitude towards technology
* Cluster 2 consists of members having mixed attitudes towards technology
* Cluster 3 consists of members having consistently high negative attitude towards technology

```{r cluster-go}
cluster_go <- geq_scoring_go[, .(Count = .N), keyby = .(Group)] %>%
                           .[, .(Group, Count, 
                                 Percentage = round(Count * 100 / nrow(geq_scoring_go), 1))]

cluster_go %>%
  kable(align = c("l", "c", "c"), 
        caption = "Cluster Breakdown for Oculus Go VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

```{r cluster-rift}
cluster_rift <- geq_scoring_rift[, .(Count = .N), keyby = .(Group)] %>% 
                               .[, .(Group, Count, Percentage = round(Count * 100 / nrow(geq_scoring_rift), 1))]

cluster_rift %>%
  kable(align = c("l", "c", "c"), 
        caption = "Cluster Breakdown for Oculus Rift VR Headset Users") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = F, latex_options = "hold_position")
```

\clearpage

```{r gender-cluster-go}
df <- geq_scoring_go %>%
  select(Group, Gender) %>%
  group_by(Group, Gender) %>%
  mutate(Count = n(), Percentage = round((Count / nrow(geq_scoring_go) * 100), 2)) %>%
  unique()
  
ggplot(df, aes(Group, y = Percentage, fill = Gender)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Cluster", y = "Percentage", 
       title = "Gender Breakdown by Cluster\nfor Oculus Go VR Users") +
  scale_fill_manual(name = "Gender", values = c(uhg1, uhg2)) +
  theme_joy_s
```

<!-- Adding extra spaces between plots -->
\vspace{1em} 

```{r age-cluster-go}
df <- geq_scoring_go %>%
  select(Group, Age) %>%
  group_by(Group, Age) %>%
  mutate(Count = n(), Percentage = round((Count / nrow(geq_scoring_go) * 100), 2)) %>%
  unique()
  
ggplot(df, aes(Group, y = Percentage, fill = Age)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Cluster", y = "Percentage", 
       title = "Age Group Breakdown by Cluster\nfor Oculus Go VR Users") +
  scale_fill_manual(name = "Age Group", values = c(uhg1, uhg2, uhg3, uhg4, uhg5, uhg6)) +
  theme_joy_s
```

\clearpage

```{r gender-cluster-rift}
df <- geq_scoring_rift %>%
  select(Group, Gender) %>%
  group_by(Group, Gender) %>%
  mutate(Count = n(), Percentage = round((Count / nrow(geq_scoring_rift) * 100), 2)) %>%
  unique()
  
ggplot(df, aes(Group, y = Percentage, fill = Gender)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Cluster", y = "Percentage", 
       title = "Gender Breakdown by Cluster\nfor Oculus Rift VR Users") +
  scale_fill_manual(name = "Gender", values = c(uhg1, uhg2)) +
  theme_joy_s
```

\vspace{1em} 

```{r age-cluster-rift}
df <- geq_scoring_rift %>%
  select(Group, Age) %>%
  group_by(Group, Age) %>%
  mutate(Count = n(), Percentage = round((Count / nrow(geq_scoring_rift) * 100), 2)) %>%
  unique()
  
ggplot(df, aes(Group, y = Percentage, fill = Age)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Cluster", y = "Percentage", 
       title = "Age Group Breakdown by Cluster\nfor Oculus Rift VR Users") +
  scale_fill_manual(name = "Age Group", values = c(uhg1, uhg2, uhg3, uhg4, uhg5, uhg6)) +
  theme_joy_s
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge In-game Components - Oculus Go}
\vfill

\clearpage

```{r boxplot-in-game-components-1-2-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$IGC1 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Competence", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_go$IGC2 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Sensory and Imaginative\nImmersion", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em} 

```{r boxplot-in-game-components-3-4-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$IGC3 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Flow", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_go$IGC4 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Tension", col = c(uhg3, uhg2, uhg4))
```

\clearpage

```{r boxplot-in-game-components-7-6-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$IGC7 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Positive Affect", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_go$IGC6 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Negative Affect", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em}

```{r boxplot-in-game-components-5-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$IGC5 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Challenge", col = c(uhg3, uhg2, uhg4))
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge Post-game Components - Oculus Go}
\vfill

\clearpage

```{r boxplot-post-game-components-1-2-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$PGC1 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Positive Experience", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_go$PGC2 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Negative Experience", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em}

```{r boxplot-post-game-components-3-4-go}
par(mfrow = c(1, 2))
boxplot(geq_scoring_go$PGC3 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Tiredness", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_go$PGC4 ~ geq_scoring_go$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Returning to Reality", col = c(uhg3, uhg2, uhg4))
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge In-game Components - Oculus Rift}
\vfill

\clearpage

```{r boxplot-in-game-components-1-2-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$IGC1 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Competence", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_rift$IGC2 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Sensory and Imaginative\nImmersion", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em} 

```{r boxplot-in-game-components-3-4-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$IGC3 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Flow", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_rift$IGC4 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Tension", col = c(uhg3, uhg2, uhg4))
```

\clearpage

```{r boxplot-in-game-components-7-6-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$IGC7 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Positive Affect", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_rift$IGC6 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Negative Affect", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em}

```{r boxplot-in-game-components-5-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$IGC5 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Challenge", col = c(uhg3, uhg2, uhg4))
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge Post-game Components - Oculus Rift}
\vfill

\clearpage

```{r boxplot-post-game-components-1-2-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$PGC1 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Positive Experience", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_rift$PGC2 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Negative Experience", col = c(uhg3, uhg2, uhg4))
```

\vspace{1em}

```{r boxplot-post-game-components-3-4-rift}
par(mfrow = c(1, 2))
boxplot(geq_scoring_rift$PGC3 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Tiredness", col = c(uhg3, uhg2, uhg4))
boxplot(geq_scoring_rift$PGC4 ~ geq_scoring_rift$Group,
        xlab = "Cluster", ylab = "Average Score", ylim = c(0, 5),
        main = "Returning to Reality", col = c(uhg3, uhg2, uhg4))
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge In-game Module - Oculus Go}
\vfill

\clearpage

```{r in-game-go-q1-age}
plot_age(geq_scoring_go, Q1_1, "Q1_1", geq = 1, i = 1)
```

\vspace{1em} 

```{r in-game-go-q1-gender}
plot_gender(geq_scoring_go, Q1_1, "Q1_1")
```

\clearpage

```{r in-game-go-q2-age}
plot_age(geq_scoring_go, Q1_2, "Q1_2", geq = 1, i = 2)
```

\vspace{1em}

```{r in-game-go-q2-gender}
plot_gender(geq_scoring_go, Q1_2, "Q1_2")
```

\clearpage

```{r in-game-go-q3-age}
plot_age(geq_scoring_go, Q1_3, "Q1_3", geq = 1, i = 3)
```

\vspace{1em}

```{r in-game-go-q3-gender}
plot_gender(geq_scoring_go, Q1_3, "Q1_3")
```

\clearpage

```{r in-game-go-q4-age}
plot_age(geq_scoring_go, Q1_4, "Q1_4", geq = 1, i = 4)
```

\vspace{1em}

```{r in-game-go-q4-gender}
plot_gender(geq_scoring_go, Q1_4, "Q1_4")
```

\clearpage

```{r in-game-go-q5-age}
plot_age(geq_scoring_go, Q1_5, "Q1_5", geq = 1, i = 5)
```

\vspace{1em}

```{r in-game-go-q5-gender}
plot_gender(geq_scoring_go, Q1_5, "Q1_5")
```

\clearpage

```{r in-game-go-q6-age}
plot_age(geq_scoring_go, Q1_6, "Q1_6", geq = 1, i = 6)
```

\vspace{1em}

```{r in-game-go-q6-gender}
plot_gender(geq_scoring_go, Q1_6, "Q1_6")
```

\clearpage

```{r in-game-go-q7-age}
plot_age(geq_scoring_go, Q1_7, "Q1_7", geq = 1, i = 7)
```

\vspace{1em}

```{r in-game-go-q7-gender}
plot_gender(geq_scoring_go, Q1_7, "Q1_7")
```

\clearpage

```{r in-game-go-q8-age}
plot_age(geq_scoring_go, Q1_8, "Q1_8", geq = 1, i = 8)
```

\vspace{1em}

```{r in-game-go-q8-gender}
plot_gender(geq_scoring_go, Q1_8, "Q1_8")
```

\clearpage

```{r in-game-go-q9-age}
plot_age(geq_scoring_go, Q1_9, "Q1_9", geq = 1, i = 9)
```

\vspace{1em}

```{r in-game-go-q9-gender}
plot_gender(geq_scoring_go, Q1_9, "Q1_9")
```

\clearpage

```{r in-game-go-q10-age}
plot_age(geq_scoring_go, Q1_10, "Q1_10", geq = 1, i = 10)
```

\vspace{1em}

```{r in-game-go-q10-gender}
plot_gender(geq_scoring_go, Q1_10, "Q1_10")
```

\clearpage

```{r in-game-go-q11-age}
plot_age(geq_scoring_go, Q1_11, "Q1_11", geq = 1, i = 11)
```

\vspace{1em}

```{r in-game-go-q11-gender}
plot_gender(geq_scoring_go, Q1_11, "Q1_11")
```

\clearpage

```{r in-game-go-q12-age}
plot_age(geq_scoring_go, Q1_12, "Q1_12", geq = 1, i = 12)
```

\vspace{1em}

```{r in-game-go-q12-gender}
plot_gender(geq_scoring_go, Q1_12, "Q1_12")
```

\clearpage

```{r in-game-go-q13-age}
plot_age(geq_scoring_go, Q1_13, "Q1_13", geq = 1, i = 13)
```

\vspace{1em}

```{r in-game-go-q13-gender}
plot_gender(geq_scoring_go, Q1_13, "Q1_13")
```

\clearpage

```{r in-game-go-q14-age}
plot_age(geq_scoring_go, Q1_14, "Q1_14", geq = 1, i = 14)
```

\vspace{1em}

```{r in-game-go-q14-gender}
plot_gender(geq_scoring_go, Q1_14, "Q1_14")
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge In-game Module - Oculus Rift}
\vfill

\clearpage

```{r in-game-rift-q1-age}
plot_age(geq_scoring_rift, Q1_1, "Q1_1", geq = 1, i = 1)
```

\vspace{1em} 

```{r in-game-rift-q1-gender}
plot_gender(geq_scoring_rift, Q1_1, "Q1_1")
```

\clearpage

```{r in-game-rift-q2-age}
plot_age(geq_scoring_rift, Q1_2, "Q1_2", geq = 1, i = 2)
```

\vspace{1em}

```{r in-game-rift-q2-gender}
plot_gender(geq_scoring_rift, Q1_2, "Q1_2")
```

\clearpage

```{r in-game-rift-q3-age}
plot_age(geq_scoring_rift, Q1_3, "Q1_3", geq = 1, i = 3)
```

\vspace{1em}

```{r in-game-rift-q3-gender}
plot_gender(geq_scoring_rift, Q1_3, "Q1_3")
```

\clearpage

```{r in-game-rift-q4-age}
plot_age(geq_scoring_rift, Q1_4, "Q1_4", geq = 1, i = 4)
```

\vspace{1em}

```{r in-game-rift-q4-gender}
plot_gender(geq_scoring_rift, Q1_4, "Q1_4")
```

\clearpage

```{r in-game-rift-q5-age}
plot_age(geq_scoring_rift, Q1_5, "Q1_5", geq = 1, i = 5)
```

\vspace{1em}

```{r in-game-rift-q5-gender}
plot_gender(geq_scoring_rift, Q1_5, "Q1_5")
```

\clearpage

```{r in-game-rift-q6-age}
plot_age(geq_scoring_rift, Q1_6, "Q1_6", geq = 1, i = 6)
```

\vspace{1em}

```{r in-game-rift-q6-gender}
plot_gender(geq_scoring_rift, Q1_6, "Q1_6")
```

\clearpage

```{r in-game-rift-q7-age}
plot_age(geq_scoring_rift, Q1_7, "Q1_7", geq = 1, i = 7)
```

\vspace{1em}

```{r in-game-rift-q7-gender}
plot_gender(geq_scoring_rift, Q1_7, "Q1_7")
```

\clearpage

```{r in-game-rift-q8-age}
plot_age(geq_scoring_rift, Q1_8, "Q1_8", geq = 1, i = 8)
```

\vspace{1em}

```{r in-game-rift-q8-gender}
plot_gender(geq_scoring_rift, Q1_8, "Q1_8")
```

\clearpage

```{r in-game-rift-q9-age}
plot_age(geq_scoring_rift, Q1_9, "Q1_9", geq = 1, i = 9)
```

\vspace{1em}

```{r in-game-rift-q9-gender}
plot_gender(geq_scoring_rift, Q1_9, "Q1_9")
```

\clearpage

```{r in-game-rift-q10-age}
plot_age(geq_scoring_rift, Q1_10, "Q1_10", geq = 1, i = 10)
```

\vspace{1em}

```{r in-game-rift-q10-gender}
plot_gender(geq_scoring_rift, Q1_10, "Q1_10")
```

\clearpage

```{r in-game-rift-q11-age}
plot_age(geq_scoring_rift, Q1_11, "Q1_11", geq = 1, i = 11)
```

\vspace{1em}

```{r in-game-rift-q11-gender}
plot_gender(geq_scoring_rift, Q1_11, "Q1_11")
```

\clearpage

```{r in-game-rift-q12-age}
plot_age(geq_scoring_rift, Q1_12, "Q1_12", geq = 1, i = 12)
```

\vspace{1em}

```{r in-game-rift-q12-gender}
plot_gender(geq_scoring_rift, Q1_12, "Q1_12")
```

\clearpage

```{r in-game-rift-q13-age}
plot_age(geq_scoring_rift, Q1_13, "Q1_13", geq = 1, i = 13)
```

\vspace{1em}

```{r in-game-rift-q13-gender}
plot_gender(geq_scoring_rift, Q1_13, "Q1_13")
```

\clearpage

```{r in-game-rift-q14-age}
plot_age(geq_scoring_rift, Q1_14, "Q1_14", geq = 1, i = 14)
```

\vspace{1em}

```{r in-game-rift-q14-gender}
plot_gender(geq_scoring_rift, Q1_14, "Q1_14")
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge Post-game Module - Oculus Go}
\vfill

\clearpage

```{r post-game-go-q1-age}
plot_age(geq_scoring_go, Q2_1, "Q2_1", geq = 2, i = 1)
```

\vspace{1em} 

```{r post-game-go-q1-gender}
plot_gender(geq_scoring_go, Q2_1, "Q2_1")
```

\clearpage

```{r post-game-go-q2-age}
plot_age(geq_scoring_go, Q2_2, "Q2_2", geq = 2, i = 2)
```

\vspace{1em}

```{r post-game-go-q2-gender}
plot_gender(geq_scoring_go, Q2_2, "Q2_2")
```

\clearpage

```{r post-game-go-q3-age}
plot_age(geq_scoring_go, Q2_3, "Q2_3", geq = 2, i = 3)
```

\vspace{1em}

```{r post-game-go-q3-gender}
plot_gender(geq_scoring_go, Q2_3, "Q2_3")
```

\clearpage

```{r post-game-go-q4-age}
plot_age(geq_scoring_go, Q2_4, "Q2_4", geq = 2, i = 4)
```

\vspace{1em}

```{r post-game-go-q4-gender}
plot_gender(geq_scoring_go, Q2_4, "Q2_4")
```

\clearpage

```{r post-game-go-q5-age}
plot_age(geq_scoring_go, Q2_5, "Q2_5", geq = 2, i = 5)
```

\vspace{1em}

```{r post-game-go-q5-gender}
plot_gender(geq_scoring_go, Q2_5, "Q2_5")
```

\clearpage

```{r post-game-go-q6-age}
plot_age(geq_scoring_go, Q2_6, "Q2_6", geq = 2, i = 6)
```

\vspace{1em}

```{r post-game-go-q6-gender}
plot_gender(geq_scoring_go, Q2_6, "Q2_6")
```

\clearpage

```{r post-game-go-q7-age}
plot_age(geq_scoring_go, Q2_7, "Q2_7", geq = 2, i = 7)
```

\vspace{1em}

```{r post-game-go-q7-gender}
plot_gender(geq_scoring_go, Q2_7, "Q2_7")
```

\clearpage

```{r post-game-go-q8-age}
plot_age(geq_scoring_go, Q2_8, "Q2_8", geq = 2, i = 8)
```

\vspace{1em}

```{r post-game-go-q8-gender}
plot_gender(geq_scoring_go, Q2_8, "Q2_8")
```

\clearpage

```{r post-game-go-q9-age}
plot_age(geq_scoring_go, Q2_9, "Q2_9", geq = 2, i = 9)
```

\vspace{1em}

```{r post-game-go-q9-gender}
plot_gender(geq_scoring_go, Q2_9, "Q2_9")
```

\clearpage

```{r post-game-go-q10-age}
plot_age(geq_scoring_go, Q2_10, "Q2_10", geq = 2, i = 10)
```

\vspace{1em}

```{r post-game-go-q10-gender}
plot_gender(geq_scoring_go, Q2_10, "Q2_10")
```

\clearpage

```{r post-game-go-q11-age}
plot_age(geq_scoring_go, Q2_11, "Q2_11", geq = 2, i = 11)
```

\vspace{1em}

```{r post-game-go-q11-gender}
plot_gender(geq_scoring_go, Q2_11, "Q2_11")
```

\clearpage

```{r post-game-go-q12-age}
plot_age(geq_scoring_go, Q2_12, "Q2_12", geq = 2, i = 12)
```

\vspace{1em}

```{r post-game-go-q12-gender}
plot_gender(geq_scoring_go, Q2_12, "Q2_12")
```

\clearpage

```{r post-game-go-q13-age}
plot_age(geq_scoring_go, Q2_13, "Q2_13", geq = 2, i = 13)
```

\vspace{1em}

```{r post-game-go-q13-gender}
plot_gender(geq_scoring_go, Q2_13, "Q2_13")
```

\clearpage

```{r post-game-go-q14-age}
plot_age(geq_scoring_go, Q2_14, "Q2_14", geq = 2, i = 14)
```

\vspace{1em}

```{r post-game-go-q14-gender}
plot_gender(geq_scoring_go, Q2_14, "Q2_14")
```

\clearpage

```{r post-game-go-q15-age}
plot_age(geq_scoring_go, Q2_15, "Q2_15", geq = 2, i = 15)
```

\vspace{1em}

```{r post-game-go-q15-gender}
plot_gender(geq_scoring_go, Q2_15, "Q2_15")
```

\clearpage

```{r post-game-go-q16-age}
plot_age(geq_scoring_go, Q2_16, "Q2_16", geq = 2, i = 16)
```

\vspace{1em}

```{r post-game-go-q16-gender}
plot_gender(geq_scoring_go, Q2_16, "Q2_16")
```

\clearpage

```{r post-game-go-q17-age}
plot_age(geq_scoring_go, Q2_17, "Q2_17", geq = 2, i = 17)
```

\vspace{1em}

```{r post-game-go-q17-gender}
plot_gender(geq_scoring_go, Q2_17, "Q2_17")
```

\clearpage

\vspace*{\fill}
\noindent
\makebox[\textwidth]{\Huge Post-game Module - Oculus Rift}
\vfill

\clearpage

```{r post-game-rift-q1-age}
plot_age(geq_scoring_rift, Q2_1, "Q2_1", geq = 2, i = 1)
```

\vspace{1em} 

```{r post-game-rift-q1-gender}
plot_gender(geq_scoring_rift, Q2_1, "Q2_1")
```

\clearpage

```{r post-game-rift-q2-age}
plot_age(geq_scoring_rift, Q2_2, "Q2_2", geq = 2, i = 2)
```

\vspace{1em}

```{r post-game-rift-q2-gender}
plot_gender(geq_scoring_rift, Q2_2, "Q2_2")
```

\clearpage

```{r post-game-rift-q3-age}
plot_age(geq_scoring_rift, Q2_3, "Q2_3", geq = 2, i = 3)
```

\vspace{1em}

```{r post-game-rift-q3-gender}
plot_gender(geq_scoring_rift, Q2_3, "Q2_3")
```

\clearpage

```{r post-game-rift-q4-age}
plot_age(geq_scoring_rift, Q2_4, "Q2_4", geq = 2, i = 4)
```

\vspace{1em}

```{r post-game-rift-q4-gender}
plot_gender(geq_scoring_rift, Q2_4, "Q2_4")
```

\clearpage

```{r post-game-rift-q5-age}
plot_age(geq_scoring_rift, Q2_5, "Q2_5", geq = 2, i = 5)
```

\vspace{1em}

```{r post-game-rift-q5-gender}
plot_gender(geq_scoring_rift, Q2_5, "Q2_5")
```

\clearpage

```{r post-game-rift-q6-age}
plot_age(geq_scoring_rift, Q2_6, "Q2_6", geq = 2, i = 6)
```

\vspace{1em}

```{r post-game-rift-q6-gender}
plot_gender(geq_scoring_rift, Q2_6, "Q2_6")
```

\clearpage

```{r post-game-rift-q7-age}
plot_age(geq_scoring_rift, Q2_7, "Q2_7", geq = 2, i = 7)
```

\vspace{1em}

```{r post-game-rift-q7-gender}
plot_gender(geq_scoring_rift, Q2_7, "Q2_7")
```

\clearpage

```{r post-game-rift-q8-age}
plot_age(geq_scoring_rift, Q2_8, "Q2_8", geq = 2, i = 8)
```

\vspace{1em}

```{r post-game-rift-q8-gender}
plot_gender(geq_scoring_rift, Q2_8, "Q2_8")
```

\clearpage

```{r post-game-rift-q9-age}
plot_age(geq_scoring_rift, Q2_9, "Q2_9", geq = 2, i = 9)
```

\vspace{1em}

```{r post-game-rift-q9-gender}
plot_gender(geq_scoring_rift, Q2_9, "Q2_9")
```

\clearpage

```{r post-game-rift-q10-age}
plot_age(geq_scoring_rift, Q2_10, "Q2_10", geq = 2, i = 10)
```

\vspace{1em}

```{r post-game-rift-q10-gender}
plot_gender(geq_scoring_rift, Q2_10, "Q2_10")
```

\clearpage

```{r post-game-rift-q11-age}
plot_age(geq_scoring_rift, Q2_11, "Q2_11", geq = 2, i = 11)
```

\vspace{1em}

```{r post-game-rift-q11-gender}
plot_gender(geq_scoring_rift, Q2_11, "Q2_11")
```

\clearpage

```{r post-game-rift-q12-age}
plot_age(geq_scoring_rift, Q2_12, "Q2_12", geq = 2, i = 12)
```

\vspace{1em}

```{r post-game-rift-q12-gender}
plot_gender(geq_scoring_rift, Q2_12, "Q2_12")
```

\clearpage

```{r post-game-rift-q13-age}
plot_age(geq_scoring_rift, Q2_13, "Q2_13", geq = 2, i = 13)
```

\vspace{1em}

```{r post-game-rift-q13-gender}
plot_gender(geq_scoring_rift, Q2_13, "Q2_13")
```

\clearpage

```{r post-game-rift-q14-age}
plot_age(geq_scoring_rift, Q2_14, "Q2_14", geq = 2, i = 14)
```

\vspace{1em}

```{r post-game-rift-q14-gender}
plot_gender(geq_scoring_rift, Q2_14, "Q2_14")
```

\clearpage

```{r post-game-rift-q15-age}
plot_age(geq_scoring_rift, Q2_15, "Q2_15", geq = 2, i = 15)
```

\vspace{1em}

```{r post-game-rift-q15-gender}
plot_gender(geq_scoring_rift, Q2_15, "Q2_15")
```

\clearpage

```{r post-game-rift-q16-age}
plot_age(geq_scoring_rift, Q2_16, "Q2_16", geq = 2, i = 16)
```

\vspace{1em}

```{r post-game-rift-q16-gender}
plot_gender(geq_scoring_rift, Q2_16, "Q2_16")
```

\clearpage

```{r post-game-rift-q17-age}
plot_age(geq_scoring_rift, Q2_17, "Q2_17", geq = 2, i = 17)
```

\vspace{1em}

```{r post-game-rift-q17-gender}
plot_gender(geq_scoring_rift, Q2_17, "Q2_17")
```



